---
title: "2019 election results for The Nationals"
author: 
date: 
output:
  xaringan::moon_reader:
    css: ["default", "libs/mjc-css/mjc-theme.css", "libs/mjc-css/mjc-fonts.css"]
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height = 5)

library(knitr)

source("election_2019.R")
```

# Primary votes by party

- The Nationals held their primary vote at the 2019 election despite significant swings to One Nation and the United Australia Party. The Liberal and Labor parties experienced swings away from them. 

``` {r fig.height = 4}
p_party_swing$`2019`
```

---

# Primary votes over last decade
  
``` {r }
grid.arrange(p_party$`2019`, p_party$`2016`, p_party$`2013`, p_party$`2010`, ncol = 2)
```

---
  
# Liberals v Nationals over last decade

- Since the 2013 landslide election the Nationals party has held its primary vote with only a small decrease. In comparison, the Liberal party primary vote has fallen by just over 10 per cent. 

NB: This is in percentage terms not "percentage point" terms. 
  
``` {r fig.height = 3.5}
p_coalition
```

---
  
# Nationals primary vote over time

- The Nationals party has been on a consistent postive trend in its primary vote since the 1998 election. We have sucesfully withstood the second coming of One Nation.
  
``` {r fig.height = 4}
p_nats_prim
```

---
  
# Nationals seats 
  
``` {r }
grid.arrange(p_nats_seats, p_nats_prop, ncol = 1)
```

---
  
# Primary votes in Nationals electorates
  
``` {r }
p_nats_elec
```

---
  
# Primary vote swings in Nationals electorates

- The Nationals acheived a positive swing in 19 of the 31 seats we ran in.
  
``` {r fig.height = 4}
p_nats_swing
```

---

# TPP votes in Nationals electorates
  
``` {r }
p_nats_tpp
```

---
  
# TPP vote swings in Nationals electorates

- The Nationals acheived a positive swing in 12 of the 16 seats where we are in the final two party preferred count.
  
``` {r fig.height = 4}
p_nats_swing_tpp
```

