---
title: "2019 election results for The Nationals"
author: 
date: 
output:
  xaringan::moon_reader:
    css: ["default", "libs/mjc-css/mjc-theme.css", "libs/mjc-css/mjc-fonts.css"]
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height = 5)

library(knitr)

source("election_2019.R")
```

# Primary votes by party

- The Nationals were the only major party to receive a positive swing at the 2019 election - albeit a small one of 0.3 per cent. 

- The Nationals party is the only major party to have received positive swings over the past 3 elections.

``` {r fig.height = 3.5}
p_party_swing$`2019`
```

---

# Primary votes over last decade
  
``` {r }
grid.arrange(p_party$`2019`, p_party$`2016`, p_party$`2013`, p_party$`2010`, ncol = 2)
```

---
  
# Liberals v Nationals over last decade

- Since the 2013 landslide election the Nationals party has consolidated its primary vote and increased it by 5 per cent. In comparison, the Liberal party primary vote has fallen by just over 10 per cent. 

NB: This is in percentage terms not "percentage point" terms. 
  
``` {r fig.height = 3.5}
p_coalition
```

---
  
# Nationals primary vote over time

- The Nationals party has been on a consistent postive trend in its primary vote since the 1998 election. We have sucesfully withstood the second coming of One Nation.
  
``` {r fig.height = 4}
p_nats_prim
```

---
  
# Nationals seats and proportion of Coalition over time
  
``` {r fig.height = 3.5}
grid.arrange(p_nats_seats, p_nats_prop, ncol = 1)
```

NB: Assumes Perin Davey is elected as a NSW Senator.
---
  
# Primary votes in Nationals electorates
  
``` {r }
p_nats_elec
```

---
  
# Primary vote swings in Nationals electorates

- The Nationals acheived a positive swing in 19 of the 31 seats we ran in.
  
``` {r fig.height = 4}
p_nats_swing
```

---

# TPP votes in Nationals electorates
  
``` {r }
p_nats_tpp
```

---
  
# TPP vote swings in Nationals electorates

- The Nationals acheived a positive swing in 10 of the 13 seats where we are in the final two party preferred count.

NB: This only includes seats were a the AEC has calculaated a TPP between the LNP and ALP. For example, such a count for Maranoa or New England has not yet been completed.
  
``` {r fig.height = 3}
p_nats_swing_tpp
```

---

# TCP votes in Nationals electorates

- The Nationals no longer hold a seat that fits within the traditional defintion of marginal, that is less than 5 per cent margin.
  
``` {r fig.height = 4}
p_nats_tcp
```

---
  
# TCP vote swings in Nationals electorates

- The independent challengers did not perform well against the Nationals. Rob Oakeshott fell 7.3 per cent short, and in Maranoa and New England, One Nation and independent canidates were beaten by more than 20 per cent.

  
``` {r fig.height = 3.5}
p_nats_swing_tcp
```

